---
title: "famcomparisions"
author: "Renuka"
date: "2023-05-08"
output: html_document
---

## G2-G2 male and female with BC without location


```{r g2g2, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
library(ggsignif)

fam_tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
tse <- transformCounts(fam_tse, method = "relabundance")
tse <- runMDS(tse, FUN = vegan::vegdist, method = "bray", name = "bray", exprs_values = "relabundance")
do <- assay(tse, "relabundance")
di <- as.matrix(vegdist(t(do), method="bray"))
# subsetting and filtering data
subset_tse <- tse[ , tse$G %in% "G2"]
subset_tse <- subset_tse[,!(colnames(subset_tse) %in% c("B2", "D2"))]
##
tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
di <- as.matrix(vegdist(t(assay(tse, "counts")), method="bray"))
di <- reshape2::melt(di) %>% `colnames<-`(c("X","Y", "value"))
# subsetting and filtering data
tse <- tse[ , tse$G %in% "G2"]
tse <- tse[,!(colnames(tse) %in% c("B2", "D2"))]

set.seed(123)
within_pairs <- colData(tse) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 

#inverted#between_pairs <- data.frame(pair_1=within_pairs$pair_1, pair_2=rev(within_pairs$pair_2))
rand <- sample(nrow(within_pairs))
between_pairs <- data.frame(pair_1=within_pairs$pair_1, pair_2=within_pairs$pair_2[rand])

rbind(
    merge(di, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(di, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)%>% ggplot(aes(x=grp,y=value))+
    geom_boxplot(outlier.shape = NA)+
    geom_jitter(width= 0.05, size= 1.7)+
    geom_signif(comparisons = list(c("within_pairs", "between_pairs")), map_signif_level = TRUE) + theme(text = element_text(size = 5)) + labs(x = "", y= "Bray-Curtis index", title = "G2-G2 unrelated comparisions") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)
```

G2 AND G1 each member- related comparision without location

```{r g2g1, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(ggsignif)
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
library(magrittr)
tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
dif <- as.matrix(vegdist(t(assay(tse, "counts")), method="bray"))
dif <- reshape2::melt(dif) %>% `colnames<-`(c("X","Y", "value"))

# subsetting and filtering data for g2 single member
tse1 <- tse[ , tse$G %in% "G2"]
tse1 <- tse1[,!(colnames(tse1) %in% c("B2", "D2"))]
tse1 <- tse1[ , tse1$Gender %in% "Male"]

# subsetting and filtering data for g1 single member
tse2 <- tse[ , tse$G %in% "G1"]
tse2 <- tse2[,!(colnames(tse2) %in% c("B1", "C2", "D1", "G2", "H2", "I2", "J2", "O2", "O3", "O4"))]
#tse2 <- tse2[,!(colnames(tse2) %in% c("B1", "D1" ,"O3"))]
#tse2 <- tse2[ , tse2$Gender %in% "Female"]

##merging two tse
tse3 <- mergeSEs(list(tse1, tse2), join = "inner")

set.seed(123)
within_pairs <- colData(tse3) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 

#between_pairs <- data.frame(pair_1=within_pairs$pair_1, pair_2=rev(within_pairs$pair_2))
rand <- sample(nrow(between_pairs))
between_pairs <- data.frame(pair_1=within_pairs$pair_1, pair_2=within_pairs$pair_2[rand])




#between_pairs <- lapply(unique(colData(tse3)$Family), function(fam) {
#    set.seed(123)
#    pair_1 <- colData(tse3) %>% as_tibble() %>% 
#    filter(Family==fam) %>% sample_n(1)
 #   set.seed(123)
#    pair_2 <- colData(tse3) %>% as_tibble() %>% 
#    filter(Family!=fam) %>% sample_n(1)
#    c(pair_1$Sample, pair_2$Sample)
#}) %>% do.call(rbind, .) %>% 
#    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2"))

rbind(
    merge(dif, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(dif, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)%>% ggplot(aes(x=grp,y=value))+
    geom_boxplot(outlier.shape = NA)+
    geom_jitter(width= 0.05, size= 1.7)+
    geom_signif(comparisons = list(c("within_pairs", "between_pairs")),map_signif_level = TRUE) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "G2-G1 related comparisions") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)
```


G2 AND G3 each member- related comparision without location

```{r g2g3, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(ggsignif)
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
library(magrittr)
tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
dif <- as.matrix(vegdist(t(assay(tse, "counts")), method="bray"))
dif <- reshape2::melt(dif) %>% `colnames<-`(c("X","Y", "value"))

# subsetting and filtering data for g2 single member
tse4 <- tse[ , tse$G %in% "G2"]
tse4 <- tse4[,!(colnames(tse4) %in% c("B2", "D2"))]
tse4 <- tse4[ , tse4$Gender %in% "Male"]

# subsetting and filtering data for g1 single member
tse5 <- tse[ , tse$G %in% "G3"]
tse5 <- tse5[,!(colnames(tse5) %in% c("A5", "B3", "D3", "F5", "I6", "K5", "M5", "N5"))]
#tse2 <- tse2[,!(colnames(tse2) %in% c("B1", "D1" ,"O3"))]
#tse2 <- tse2[ , tse2$Gender %in% "Female"]

##merging two tse
tse6 <- mergeSEs(list(tse4, tse5), join = "inner")

set.seed(123)
within_pairs <- colData(tse6) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 

rand <- sample(nrow(between_pairs))
between_pairs <- data.frame(pair_1=within_pairs$pair_1, pair_2=within_pairs$pair_2[rand])


rbind(
    merge(dif, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(dif, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)%>% ggplot(aes(x=grp,y=value))+
    geom_boxplot(outlier.shape = NA)+
    geom_jitter(width= 0.05, size= 1.7)+
    geom_signif(comparisons = list(c("within_pairs", "between_pairs")),map_signif_level = TRUE) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "G2-G3 related comparisions") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)
```


Location-wise G2 couple- unrlated comparisions

```{r Lg2g2, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(ggsignif)
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
library(magrittr)
tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
di <- as.matrix(vegdist(t(assay(tse, "counts")), method="bray"))
di <- reshape2::melt(di) %>% `colnames<-`(c("X","Y", "value"))

tse_list <- splitOn(tse, f= "Location")
tse_Ahmednagar <- tse_list[[1]]
tse_Pune <- tse_list[[2]]

# subsetting and filtering data
tse_Ahmednagar <- tse_Ahmednagar[ , tse_Ahmednagar$G %in% "G2"]
tse_Ahmednagar <- tse_Ahmednagar[,!(colnames(tse_Ahmednagar) %in% c("B2", "D2"))]

set.seed(123)
within_pairs <- colData(tse_Ahmednagar) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 
rand <- sample(nrow(within_pairs))
between_pairs <- data.frame(pair_1=within_pairs$pair_1, pair_2=within_pairs$pair_2[rand])

#between_pairs <- lapply(unique(colData(tse_Ahmednagar)$Family), function(fam) {
#    set.seed(123)
#    pair_1 <- colData(tse_Ahmednagar) %>% as_tibble() %>% 
#    filter(Family==fam) %>% sample_n(1)
#    set.seed(123)
#    pair_2 <- colData(tse_Ahmednagar) %>% as_tibble() %>% 
#    filter(Family!=fam & Gender!=pair_1$Gender) %>% sample_n(1)
#    c(pair_1$Sample, pair_2$Sample)
#}) %>% do.call(rbind, .) %>% 
#    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2"))


ANdf <- rbind(
    merge(di, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(di, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)

#ggplot(aes(x=grp,y=value))+
#    geom_boxplot(outlier.shape = NA)+
#    geom_jitter(width= 0.05, size= 1.7)+
#    geom_signif(comparisons = list(c("within_pairs", "between_pairs"))) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "3 a) Ahmednagar") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)


tse_Pune <- tse_list[[2]]
# subsetting and filtering data
tse_Pune  <- tse_Pune [ , tse_Pune$G %in% "G2"]


set.seed(123)
within_pairs <- colData(tse_Pune) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 
rand <- sample(nrow(within_pairs))
between_pairs <- data.frame(pair_1=within_pairs$pair_1, pair_2=within_pairs$pair_2[rand])

#between_pairs <- lapply(unique(colData(tse_Pune)$Family), function(fam) {
#    set.seed(123)
#    pair_1 <- colData(tse_Pune) %>% as_tibble() %>% 
#    filter(Family==fam) %>% sample_n(1)
#    set.seed(123)
#    pair_2 <- colData(tse_Pune) %>% as_tibble() %>% 
#    filter(Family!=fam & Gender!=pair_1$Gender) %>% sample_n(1)
#    c(pair_1$Sample, pair_2$Sample)
#}) %>% do.call(rbind, .) %>% 
#    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2"))


PNdf <- rbind(
    merge(di, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(di, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)

mergedcities <- rbind(ANdf, PNdf)
mergedcities$City <- c(rep("Ahmednagar", nrow(ANdf)),  rep("Pune", nrow(PNdf)))
g <- ggplot(mergedcities, aes(x=grp,y=value))+
    geom_boxplot(outlier.shape = NA)+
    geom_jitter(aes(colour = City), width= 0.05, size= 1.7) +
    geom_signif(comparisons = list(c("within_pairs", "between_pairs"))) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "Locationwise G2-G2 comparison") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)
print(g)
```



Location-wise G1-G2 related comparisons

```{r Lg2g1, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(ggsignif)
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
library(magrittr)
tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
di <- as.matrix(vegdist(t(assay(tse, "counts")), method="bray"))
di <- reshape2::melt(di) %>% `colnames<-`(c("X","Y", "value"))

tse_list <- splitOn(tse3, f= "Location")
tse_Ahmdg2g1 <- tse_list[[1]]
tse_Puneg2g1 <- tse_list[[2]]

# subsetting and filtering data
#tse_Ahmednagar <- tse_Ahmednagar[ , tse_Ahmednagar$G %in% "G2"]
#tse_Ahmednagar <- tse_Ahmednagar[,!(colnames(tse_Ahmednagar) %in% c("B2", "D2"))]

set.seed(123)
within_pairs <- colData(tse_Ahmdg2g1) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 

between_pairs <- lapply(unique(colData(tse_Ahmdg2g1)$Family), function(fam) {
    set.seed(123)
    pair_1 <- colData(tse_Ahmdg2g1) %>% as_tibble() %>% 
    filter(Family==fam) %>% sample_n(1)
    set.seed(123)
    pair_2 <- colData(tse_Ahmdg2g1) %>% as_tibble() %>% 
    filter(Family!=fam & Gender!=pair_1$Gender) %>% sample_n(1)
    c(pair_1$Sample, pair_2$Sample)
}) %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2"))


ANg2g1 <- rbind(
    merge(di, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(di, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)

#ggplot(aes(x=grp,y=value))+
#    geom_boxplot(outlier.shape = NA)+
#    geom_jitter(width= 0.05, size= 1.7)+
#    geom_signif(comparisons = list(c("within_pairs", "between_pairs"))) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "3 a) Ahmednagar") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)


#tse_Pune <- tse_list[[2]]
# subsetting and filtering data
#tse_Pune  <- tse_Pune [ , tse_Pune$G %in% "G2"]
tse_Puneg2g1 <- tse_list[[2]]

set.seed(123)
within_pairs <- colData(tse_Puneg2g1) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 

between_pairs <- lapply(unique(colData(tse_Puneg2g1)$Family), function(fam) {
    set.seed(123)
    pair_1 <- colData(tse_Puneg2g1) %>% as_tibble() %>% 
    filter(Family==fam) %>% sample_n(1)
    set.seed(123)
    pair_2 <- colData(tse_Puneg2g1) %>% as_tibble() %>% 
    filter(Family!=fam & Gender!=pair_1$Gender) %>% sample_n(1)
    c(pair_1$Sample, pair_2$Sample)
}) %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2"))


PNg2g1 <- rbind(
    merge(di, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(di, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)

mergedcities <- rbind(ANg2g1, PNg2g1)
mergedcities$City <- c(rep("Ahmednagar", nrow(ANg2g1)),  rep("Pune", nrow(PNg2g1)))
s <- ggplot(mergedcities, aes(x=grp,y=value))+
    geom_boxplot(outlier.shape = NA)+
    geom_jitter(aes(colour = City), width= 0.05, size= 1.7) +
    geom_signif(comparisons = list(c("within_pairs", "between_pairs"))) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "Location-wise G2-G1 related comparisions") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)
print(s)
```

tp
Location-wise G2-G3 related comparisions

```{r Lg2g3, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(ggsignif)
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
library(magrittr)
tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
di <- as.matrix(vegdist(t(assay(tse, "counts")), method="bray"))
di <- reshape2::melt(di) %>% `colnames<-`(c("X","Y", "value"))

tse_list <- splitOn(tse6, f= "Location")
tse_Ahmdg2g3 <- tse_list[[1]]
tse_Puneg2g3 <- tse_list[[2]]

# subsetting and filtering data
#tse_Ahmednagar <- tse_Ahmednagar[ , tse_Ahmednagar$G %in% "G2"]
#tse_Ahmednagar <- tse_Ahmednagar[,!(colnames(tse_Ahmednagar) %in% c("B2", "D2"))]

set.seed(123)
within_pairs <- colData(tse_Ahmdg2g3) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 

between_pairs <- lapply(unique(colData(tse_Ahmdg2g3)$Family), function(fam) {
    set.seed(123)
    pair_1 <- colData(tse_Ahmdg2g3) %>% as_tibble() %>% 
    filter(Family==fam) %>% sample_n(1)
    set.seed(123)
    pair_2 <- colData(tse_Ahmdg2g3) %>% as_tibble() %>% 
    filter(Family!=fam & Gender!=pair_1$Gender) %>% sample_n(1)
    c(pair_1$Sample, pair_2$Sample)
}) %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2"))


ANg2g3 <- rbind(
    merge(di, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(di, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)

#ggplot(aes(x=grp,y=value))+
#    geom_boxplot(outlier.shape = NA)+
#    geom_jitter(width= 0.05, size= 1.7)+
#    geom_signif(comparisons = list(c("within_pairs", "between_pairs"))) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "3 a) Ahmednagar") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)


#tse_Pune <- tse_list[[2]]
# subsetting and filtering data
#tse_Pune  <- tse_Pune [ , tse_Pune$G %in% "G2"]
tse_Puneg2g3 <- tse_list[[2]]

set.seed(123)
within_pairs <- colData(tse_Puneg2g3) %>% as_tibble() %>% group_by(Family) %>%
    summarise(within_pairs=combn(Sample, 2, simplify = FALSE)) %>% 
    select(within_pairs) %>% .[[1]] %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2")) 

between_pairs <- lapply(unique(colData(tse_Puneg2g3)$Family), function(fam) {
    set.seed(123)
    pair_1 <- colData(tse_Puneg2g3) %>% as_tibble() %>% 
    filter(Family==fam) %>% sample_n(1)
    set.seed(123)
    pair_2 <- colData(tse_Puneg2g3) %>% as_tibble() %>% 
    filter(Family!=fam & Gender!=pair_1$Gender) %>% sample_n(1)
    c(pair_1$Sample, pair_2$Sample)
}) %>% do.call(rbind, .) %>% 
    as.data.frame() %>% `colnames<-`(c("pair_1", "pair_2"))


PNg2g3 <- rbind(
    merge(di, within_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("within_pairs",nrow(within_pairs))),
    merge(di, between_pairs, by.x=c("X","Y"), by.y=c("pair_1", "pair_2")) %>%
        mutate(grp=rep("between_pairs",nrow(between_pairs)))
)

mergedcities <- rbind(ANg2g3, PNg2g3)
mergedcities$City <- c(rep("Ahmednagar", nrow(ANg2g3)),  rep("Pune", nrow(PNg2g3)))
s <- ggplot(mergedcities, aes(x=grp,y=value))+
    geom_boxplot(outlier.shape = NA)+
    geom_jitter(aes(colour = City), width= 0.05, size= 1.7) +
    geom_signif(comparisons = list(c("within_pairs", "between_pairs"))) + theme(text = element_text(size = 10)) + labs(x = "", y= "Bray-Curtis index", title = "Location-wise G2-G3 related comparisions") + scale_x_discrete(labels=c("within_pairs" = "Within family", "between_pairs" = "Between family")) + theme_bw(base_size = 20)
print(s)
```



Random 15 pairs- any 2 individuals without location

```{r ran, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
fam_tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
tse <- transformCounts(fam_tse, method = "relabundance")
tse <- runMDS(tse, FUN = vegan::vegdist, method = "bray", name = "bray", exprs_values = "relabundance")



## two Members of same family
d0 <- assay(tse, "relabundance")
dx <- as.matrix(vegdist(t(d0), method="bray"))
ran <- sample(1:5, 2)

###########set.seed(1234)
beta_compare <- function(families, dx) {
  
  
  if (families[[1]] == families[[2]]) {
    
    endn <- sum(str_detect(rownames(dx), families[[1]]))
    
    my_rnd <- sample(1:endn, 2)
    my_beta <- dx[paste0(families[[1]], my_rnd[[1]]), paste0(families[[2]], my_rnd[[2]])]

    first_member <- paste0(families[[1]], my_rnd[[1]])
    second_member <- paste0(families[[2]], my_rnd[[2]])
    
  } else {
    
    endn1 <- sum(str_detect(rownames(dx), families[[1]]))
    endn2 <- sum(str_detect(rownames(dx), families[[2]]))
    
    my_rnd1 <- sample(1:endn1, 1)
    my_rnd2 <- sample(1:endn2, 1)
    
    first_member <- paste0(families[[1]], my_rnd1[[1]])
    second_member <- paste0(families[[2]], my_rnd2[[1]])
    
  }
  
  my_beta <- dx[first_member, second_member]
  
  return(list(my_beta,first_member, second_member))
  
}

set.seed(2345)
beta_values <- c()
families1 <- c()
families2 <- c()

for (first_family in unique(tse$Family)){
  
  for (second_family in unique(tse$Family)){
    
    
    tmp_res <- beta_compare(c(first_family, second_family ), dx)
    beta_values <- c(beta_values, tmp_res[[1]])
    families1 <- c(families1, tmp_res[[2]])
    families2 <- c(families2, tmp_res[[3]])
     
  }
}

j <- data.frame(BetaComparison = beta_values,
           FirstFamily = families1,
           SecondFamily = families2)
j <- j %>% mutate(Within = substr(FirstFamily, 1,1) == substr(SecondFamily, 1,1))
L<- j %>% filter(Within==FALSE)
set.seed(9876)
y <- L[sample(1:nrow(L), 15), ] ##between comparisons 
only_withins <- j %>% filter(Within==TRUE)
newdf<- rbind(y, only_withins)
library(ggsignif)
H <- ggplot(newdf, aes(x = Within, y = BetaComparison)) +   
geom_boxplot(outlier.shape = NA) + geom_jitter(width=0.05) +geom_signif(comparisons = list(c("FALSE", "TRUE")), map_signif_level = FALSE) + theme(text = element_text(size = 25)) + labs(x = "", y= "Bray-Curtis index", title = "Randomly selected two members")
H1<- H + scale_x_discrete(labels=c("TRUE" = "Within family", "FALSE" = "Between family")) + theme_bw(20)
print(H1) 
```

Random 15 pairs- any 2 individuals with location

```{r ranL, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(mia)
library(vegan)
library(scater)
library(dplyr)
library(tidyverse)
fam_tse <- readRDS("inputdata/processed/TSE/fam_tse.rds")
tse <- transformCounts(fam_tse, method = "relabundance")
tse <- runMDS(tse, FUN = vegan::vegdist, method = "bray", name = "bray", exprs_values = "relabundance")



## two Members of same family
d0 <- assay(tse, "relabundance")
dx <- as.matrix(vegdist(t(d0), method="bray"))
ran <- sample(1:5, 2)
tse_list <- splitOn(tse, f= "Location")
tse_Ahmednagar <- tse_list[[1]]
tse_Pune <- tse_list[[2]]


###########set.seed(1234)
beta_compare <- function(families, dx) {
  
  
  if (families[[1]] == families[[2]]) {
    
    endn <- sum(str_detect(rownames(dx), families[[1]]))
    
    my_rnd <- sample(1:endn, 2)
    my_beta <- dx[paste0(families[[1]], my_rnd[[1]]), paste0(families[[2]], my_rnd[[2]])]

    first_member <- paste0(families[[1]], my_rnd[[1]])
    second_member <- paste0(families[[2]], my_rnd[[2]])
    
  } else {
    
    endn1 <- sum(str_detect(rownames(dx), families[[1]]))
    endn2 <- sum(str_detect(rownames(dx), families[[2]]))
    
    my_rnd1 <- sample(1:endn1, 1)
    my_rnd2 <- sample(1:endn2, 1)
    
    first_member <- paste0(families[[1]], my_rnd1[[1]])
    second_member <- paste0(families[[2]], my_rnd2[[1]])
    
  }
  
  my_beta <- dx[first_member, second_member]
  
  return(list(my_beta,first_member, second_member))
  
}

##############forAhmednagar#############
set.seed(2345)
beta_values <- c()
families1 <- c()
families2 <- c()

for (first_family in unique(tse_Ahmednagar$Family)){
  
  for (second_family in unique(tse_Ahmednagar$Family)){
    
    
    tmp_res <- beta_compare(c(first_family, second_family ), dx)
    beta_values <- c(beta_values, tmp_res[[1]])
    families1 <- c(families1, tmp_res[[2]])
    families2 <- c(families2, tmp_res[[3]])
     
  }
}

j <- data.frame(BetaComparison = beta_values,
           FirstFamily = families1,
           SecondFamily = families2)
j <- j %>% mutate(Within = substr(FirstFamily, 1,1) == substr(SecondFamily, 1,1))
L<- j %>% filter(Within==FALSE)
set.seed(9876)
y <- L[sample(1:nrow(L), 5), ] ##between comparisons 
only_withins <- j %>% filter(Within==TRUE)
A_newdf<- rbind(y, only_withins)
#library(ggsignif)
#H <- ggplot(A_newdf, aes(x = Within, y = BetaComparison)) +   
#geom_boxplot(outlier.shape = NA) + geom_jitter(width=0.05) +geom_signif(comparisons = list(c("FALSE", "TRUE")), map_signif_level = FALSE) + theme(text = element_text(size = 25)) + labs(x = "", y= "Bray-Curtis index", title = "Randomly selected two members")
#H1<- H + scale_x_discrete(labels=c("TRUE" = "Within family", "FALSE" = "Between family")) + theme_bw(20)
#print(H1) 

##############forPune#############
tse_Pune <- tse_list[[2]]
beta_compare <- function(families, dx) {
  
  
  if (families[[1]] == families[[2]]) {
    
    endn <- sum(str_detect(rownames(dx), families[[1]]))
    
    my_rnd <- sample(1:endn, 2)
    my_beta <- dx[paste0(families[[1]], my_rnd[[1]]), paste0(families[[2]], my_rnd[[2]])]

    first_member <- paste0(families[[1]], my_rnd[[1]])
    second_member <- paste0(families[[2]], my_rnd[[2]])
    
  } else {
    
    endn1 <- sum(str_detect(rownames(dx), families[[1]]))
    endn2 <- sum(str_detect(rownames(dx), families[[2]]))
    
    my_rnd1 <- sample(1:endn1, 1)
    my_rnd2 <- sample(1:endn2, 1)
    
    first_member <- paste0(families[[1]], my_rnd1[[1]])
    second_member <- paste0(families[[2]], my_rnd2[[1]])
    
  }
  
  my_beta <- dx[first_member, second_member]
  
  return(list(my_beta,first_member, second_member))
  
}


set.seed(2345)
beta_values <- c()
families1 <- c()
families2 <- c()

for (first_family in unique(tse_Pune$Family)){
  
  for (second_family in unique(tse_Pune$Family)){
    
    
    tmp_res <- beta_compare(c(first_family, second_family ), dx)
    beta_values <- c(beta_values, tmp_res[[1]])
    families1 <- c(families1, tmp_res[[2]])
    families2 <- c(families2, tmp_res[[3]])
     
  }
}

j <- data.frame(BetaComparison = beta_values,
           FirstFamily = families1,
           SecondFamily = families2)
j <- j %>% mutate(Within = substr(FirstFamily, 1,1) == substr(SecondFamily, 1,1))
L<- j %>% filter(Within==FALSE)
set.seed(9876)
y <- L[sample(1:nrow(L), 10), ] ##between comparisons 
only_withins <- j %>% filter(Within==TRUE)
P_newdf<- rbind(y, only_withins)
#library(ggsignif)
#H <- ggplot(P_newdf, aes(x = Within, y = BetaComparison)) +   
#geom_boxplot(outlier.shape = NA) + geom_jitter(width=0.05) +geom_signif(comparisons = list(c("FALSE", "TRUE")), map_signif_level = FALSE) + theme(text = element_text(size = 25)) + labs(x = "", y= "Bray-Curtis index", title = "Randomly selected two members")
#H1<- H + scale_x_discrete(labels=c("TRUE" = "Within family", "FALSE" = "Between family")) + theme_bw(20)
#print(H1) 

mergedcities <- rbind(A_newdf, P_newdf)
mergedcities$City <- c(rep("Ahmednagar", nrow(A_newdf)),  rep("Pune", nrow(P_newdf)))
C <- ggplot(mergedcities, aes(x = Within, y = BetaComparison)) +   
geom_boxplot(outlier.shape = NA) + geom_jitter(aes(colour = City),width=0.05) +geom_signif(comparisons = list(c("FALSE", "TRUE")), map_signif_level = FALSE) + theme(text = element_text(size = 25)) + labs(x = "", y= "Bray-Curtis index", title = "Randomly selected with city")
C1<- C + scale_x_discrete(labels=c("TRUE" = "Within family", "FALSE" = "Between family")) + theme_bw(20)
print(C1) 
gridExtra::grid.arrange(H1, C1, nrow = 1)
```